Artin Group Presentations Arising from Cluster Algebras

### 2014-09-08 Paper.tex
removed todos

%The package below let's us add todos to the document in a way that will stand out at a glance. It will also list all of the current things to do, with their respective page numbers on the first page of the document. You can add a todo like this:
%
% Text text text \todo{change this text to something useful!}
%
%Among other things, you can edit the color of a todo:
%
% \todo[color=\ltblue]{this todo will have a light blue background!}
%
%And you can include the todo as a line in the text, rather than in the margins:
%
% \todo[inline]{this will appear in the middle of the page}

%\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
%\def\ltblue{blue!20!white}
%\def\ltgreen{green!20!white}

@@

\makeatletter
\providecommand\@dotsep{5}
\def\listtodoname{List of Todos}
\def\listoftodos{\@starttoc{tdo}\listtodoname}
\makeatother

\begin{document}
%This adds the list of todos to the first page.
\listoftodos

\title{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
\address{Jacob: University of Notre Dame \\
Hailee: 1184 W Main St; Decatur, IL 62522}
\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
\date{\today}
\keywords{Artin group, cluster algebra, diagram representations}

@@

A \textit{cluster algebra} is an integral domain which can be generated by a set of elements called \textit{cluster variables} that satisfy certain exchange relations. Following the style of \cite{FZ02} and \cite{BM13}, we will define cluster algebras in terms of \textit{skew-symmetrisable} matrices (that is, a matrix $B$ such that there exists a diagonal matrix $D$ of the same size with $D_{ii} >0$ such that $DB$ is skew-symmetric). Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$. We will define an \textit{intial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix. Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
\begin{displaymath}
x_k^{\prime}x_k = \prod_{B_{ik} > 0}{x_i^{B_{ik}}} + \prod_{B_{ik} < 0}{x_i^{-B_{ik}}}
\end{displaymath}
Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\boldsymbol{x}, B) = (\textbf{x}^{\prime}, B^{\prime})$ where:
\begin{displaymath}
B_{ij}^{\prime} = \begin{cases} - B_{ij} & \mbox{ if } i = k \mbox{ or } j = k;\\
B_{ij} + \frac{|B_{ik}|B_{kj} + B_{ik}|B_{kj}|}{2} & \mbox{ otherwise. }\\
\end{cases}
\end{displaymath}
and $\textbf{x}^{\prime} = \left\{ x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n \right\}$.
Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = \left\{ x_1, \ldots, x_n \right\}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables. \\

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}[baseline=-0.5ex]

@@

\caption{Mutation of $\Gamma$ at a node k}\label{mutation}
\end{figure}

@@

Then, they define $W(\Gamma)$ to be the group generated by $s_i$, for $i \in \V$, under the following relations. Note that $e$ will denote the identity element of $W(\Gamma)$.
\begin{enumerate}
\item $s_i^2 = e$ for all $i$;
\item $(s_is_j)^{m_{ij}} = e$ for all $i \neq j$;
\item For any chordless cycle (as defined in Definition \ref{chordlesscycle}) $C$ in $\Gamma$, where
\begin{displaymath}
C = i_0 \xrightarrow{w_1} i_1 \xrightarrow{w_2} \cdots \xrightarrow{w_{d-1}} i_{d-1} \xrightarrow{w_0} i_0
\end{displaymath}
and all of the weights $w_k$ are $1$ or $w_0 = 2$, we have
\begin{displaymath}
(s_{i_0}s_{i_1}\cdots s_{i_{d-2}}s_{i_{d-1}}s_{i_{d-2}}\cdots s_{i_1})^2 =e.
\end{displaymath}
%\todo{Maybe it's worth presenting definition 2.4 before this, and then saying it is equivalent to removing certain the (R3)(b) relations. Don't they actually present the definition you refer to in Definition 2.4 as the presentation? You say it is an alteration there, but I think it's the original definition}
\end{enumerate}

@@

\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}} \label{fig:cycle_types}
\end{figure}

@@

\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}} \label{fig:local_three}
\end{figure}

@@

   \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    & |[name = ul]|\bullet& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ur) to node[above] {1} (ul)
  ;
  \draw[->]
  (ul) to node[left]{2}(dl)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
\draw[->]
  (dl) to node[above]{2} (ur)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
   \node [yshift = .4 cm,xshift = .4 cm] at (ur){2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
  \node [yshift = -.95 cm,xshift = .95 cm] at (ul){$C'$};
    \end{tikzpicture}
    \end{enumerate}

\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}} \label{fig:first_cycle_types}
\end{figure}

@@

\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}} \label{fig:second_cycle_types}
\end{figure}

@@

so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
\end{lem}

@@

\begin{def}\cite[Definition 4.1]{FT13}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $W_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(R1)] $s_{i}^{2} = e$ for all i = 1, \dots, n
\item[(R2)] $(s_{i}s_{j})^{m_{ij}} = e$ where 
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[(R3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of Table \ref{table1}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{def}

@@

\begin{table}[h] 
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (R4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$ \\ \hline

@@

\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $(s_{2}s_{1}s_{2}s_{1}s_{2}s_{3})^{2} = e$ and $(s_{2}s_{3}s_{2}s_{3}s_{2}s_{1})^{2} = e$ \\ \hline
\end{tabular}
\caption{(R4) Relations} \label{table1}
\end{table}

@@

\begin{defn}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $A_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(T2)] $\langle s_{i}, s_{j} \rangle^{m_{ij}} = \langle s_{j}, s_{i} \rangle^{m_{ij}}$ where
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[(T3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $\langle s_{i_{l}}p(i_{l}, i_{l+1}) \rangle^{m(l)} = \langle p(i_{l}, i_{l+1})s_{i_{l}} \rangle^{m(l)}$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[(T4)] For each subdiagram of $\Gamma$ of the form shown in the first column of Table \ref{table2}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{defn}

@@

\begin{table}[h] 
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (T4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $s_{2}s_{1}s_{2}^{-1}s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}s_{2}s_{1}s_{2}^{-1}$ \\ \hline

@@

\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $s_{2}s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1} = s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1}s_{2}$ and $s_{1}s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1} = s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1}s_{1}$ \\ \hline
\end{tabular}
\caption{(T4) Relations} \label{table2}
\end{table}

>>>>

%\def\ltblue{blue!20!white}
%\def\ltgreen{green!20!white}

@@

\begin{document}

\title{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
\date{\today}
\keywords{Artin group, cluster algebra, diagram representations}

@@

A \textit{cluster algebra} is an integral domain which can be generated by a set of elements called \textit{cluster variables} that satisfy certain exchange relations. Following the style of \cite{FZ02} and \cite{BM13}, we will define cluster algebras in terms of \textit{skew-symmetrisable} matrices (that is, a matrix $B$ such that there exists a diagonal matrix $D$ of the same size with $D_{ii} >0$ such that $DB$ is skew-symmetric). Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$. We will define an \textit{initial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix. Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
\begin{displaymath}
x_k^{\prime}x_k = \prod_{B_{ik} > 0}{x_i^{B_{ik}}} + \prod_{B_{ik} < 0}{x_i^{-B_{ik}}}
\end{displaymath}
Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\boldsymbol{x}, B) = (\textbf{x}^{\prime}, B^{\prime})$ where:
\begin{displaymath}
B_{ij}^{\prime} = \begin{cases} - B_{ij} & \mbox{ if } i = k \mbox{ or } j = k;\\
B_{ij} + \frac{|B_{ik}|B_{kj} + B_{ik}|B_{kj}|}{2} & \mbox{ otherwise. }\\
\end{cases}
\end{displaymath}
and $\textbf{x}^{\prime} = \left\{ x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n \right\}$.
Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = \left\{ x_1, \ldots, x_n \right\}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables. \\

@@

\begin{center}
\begin{tikzpicture}[baseline=-0.5ex]
\label{mutation}

@@

@@

Then, they define $W(\Gamma)$ to be the group generated by $s_i$, for $i \in \V$, under the following relations. Note that $e$ will denote the identity element of $W(\Gamma)$.
\begin{enumerate}
\item $s_i^2 = e$ for all $i$;
\item $(s_is_j)^{m_{ij}} = e$ for all $i \neq j$;
\item For any chordless cycle (as defined in Definition \ref{chordlesscycle}) $C$ in $\Gamma$, where
\begin{displaymath}
C = i_0 \xrightarrow{w_1} i_1 \xrightarrow{w_2} \cdots \xrightarrow{w_{d-1}} i_{d-1} \xrightarrow{w_0} i_0
\end{displaymath}
and all of the weights $w_k$ are $1$ or $w_0 = 2$, we have
\begin{displaymath}
(s_{i_0}s_{i_1}\cdots s_{i_{d-2}}s_{i_{d-1}}s_{i_{d-2}}\cdots s_{i_1})^2 =e.
\end{displaymath}
\end{enumerate}

@@

   \end{tikzpicture}
   \label{fig:cycle_types}
\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}}
\end{figure}

@@

\label{fig:local_three}
\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}}
\end{figure}

@@

   \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    & |[name = ul]|\bullet& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ur) to node[above] {1} (ul)
  ;
  \draw[->]
  (ul) to node[left]{2}(dl)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
\draw[->]
  (dl) to node[above]{2} (ur)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
   \node [yshift = .4 cm,xshift = .4 cm] at (ur){2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
  \node [yshift = -.95 cm,xshift = .95 cm] at (ul){$C'$};
    \end{tikzpicture}
    \end{enumerate}
\label{fig:first_cycle_types}
\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
\end{figure}

@@

\label{fig:second_cycle_types}
\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}}
\end{figure}

@@

so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satisfying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
\end{lem}

@@

\begin{def}\cite[Definition 4.1]{FT13}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $W_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(R1)] $s_{i}^{2} = e$ for all i = 1, \dots, n
\item[(R2)] $(s_{i}s_{j})^{m_{ij}} = e$ where 
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[(R3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table1}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{def}

@@

\begin{table}[h] \label{table1}
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (R4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$ \\ \hline

@@

\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $(s_{2}s_{1}s_{2}s_{1}s_{2}s_{3})^{2} = e$ and $(s_{2}s_{3}s_{2}s_{3}s_{2}s_{1})^{2} = e$ \\ \hline
\end{tabular}
\caption{(R4) Relations}
\end{table}

@@

\begin{defn}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $A_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(T2)] $\langle s_{i}, s_{j} \rangle^{m_{ij}} = \langle s_{j}, s_{i} \rangle^{m_{ij}}$ where
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[(T3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $\langle s_{i_{l}}p(i_{l}, i_{l+1}) \rangle^{m(l)} = \langle p(i_{l}, i_{l+1})s_{i_{l}} \rangle^{m(l)}$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[(T4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table2}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{defn}

@@

\begin{table}[h] \label{table2}
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (T4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $s_{2}s_{1}s_{2}^{-1}s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}s_{2}s_{1}s_{2}^{-1}$ \\ \hline

@@

\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $s_{2}s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1} = s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1}s_{2}$ and $s_{1}s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1} = s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1}s_{1}$ \\ \hline
\end{tabular}
\caption{(T4) Relations}
\end{table}
